The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-02-24 paper.tex
updated figure caption

\begin{figure*}[ht]
    \centering
    \begin{tabular}{cccc}
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw04-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw06-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw08-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw10-small} \\
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw12-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw14-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw16-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw18-small} \\
    \end{tabular}
    \caption{
        Snapshot images after smearing the visiblities over the entire 100 hour observation window.
    }
\end{figure*}

>>>>

\begin{figure*}[ht]
    \centering
    \begin{tabular}{cccc}
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw04-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw06-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw08-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw10-small} \\
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw12-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw14-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw16-small} &
        \includegraphics[width=0.22\textwidth]{figures/smeared-snapshots/spw18-small} \\
    \end{tabular}
    \caption{
        Dirty snapshot images after smearing the visiblities over the entire 100 hour observation
        window.  The two bright source tracks correspond to Cas A (top track) and Cyg A (bottom
        track) smeared along a ring of constant declination. The sources dotting the horizon are
        faulty power line insulators.
    }
\end{figure*}
